Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 reviews/reviewer2-response.md

It didn't seem to matter much. The mean velocity fields appear to be nearly
symmetrical about the $x$--$y$ plane, but nonetheless, the slip BC is at least
closer to how a free surface would behave than a no slip BC.

>Is this mesh [Figure 4] too coarse for adequate resolution of the flow?

It could be. For our mesh dependence study we held the topology fixed and scaled
the mesh proportionally. The mesh should be fine enough to resolve the boundary
layer since $y^+ \sim 1$, but it is a fair point that maybe separated flow
structures may be dissipated in an exaggerated way. However, exploring the mesh
topology parameter space would have been prohibitive.

>So the SA and SST took the same time?

Since the chosen SA time step was about half that of the SST, the SA model did
take longer to solve, though they were still the same order of magnitude. We
decided it wouldn't be useful to readers to give very specific metrics of solver
time since there could be many intervening variables, e.g., hardware.

>Did you prove that the meshing of the outer walls didn't affect the results.

We did not, but if we inspect the velocity fields, which don't extend out all
the way to the walls, gradients are very small around the outer region,
indicating the effects should be negligible.

### 2016-10-02 paper.tex
Clarify simulated second
Define z and H

Turbine operation in all cases was simulated for 10 seconds, or approximately
six rotor revolutions. Computations for the 3-D cases were run on 192 processes
(24 nodes $\times$ 8 cores each on Sandia National Labs' Red Mesa high
performance computing cluster) and took on the order of 1,000 CPU hours per
second of simulated time. The 2-D simulations were run on a single processor and
took on the order of one CPU hour per second.

@@

Mean velocity profiles at one turbine diameter downstream are shown in
Figure~\ref{fig:br-cfd-profiles}. The 2-D results suffer from a blockage
mismatch, i.e., keeping the proximity of the walls constant increases the
blockage ratio. The 3-D results, however, show good agreement with the
experiments.

@@

    \caption{Mean velocity (left) and turbulence kinetic energy (right) profiles
        at $x/D=1$ from 2-D simulations, 3-D simulations ($z/H=0$), and experiments
        \cite{Bachant2015-JoT}.}

>>>>

Turbine operation in all cases was simulated for 10 seconds, or approximately
six rotor revolutions. Computations for the 3-D cases were run on 192 processes
(24 nodes $\times$ 8 cores each on Sandia National Labs' Red Mesa high
performance computing cluster) and took on the order of 1,000 CPU hours per
second of simulated time. The 2-D simulations were run on a single processor and
took on the order of one CPU hour per simulated second.

@@

Mean velocity profiles at the mid $x$--$y$ plane (or the nondimensional vertical
coordinate $z/H=0$) one turbine diameter downstream are shown in
Figure~\ref{fig:br-cfd-profiles}. The 2-D results suffer from a blockage
mismatch, i.e., keeping the proximity of the walls constant increases the
blockage ratio. The 3-D results, however, show good agreement with the
experiments.

@@

    \caption{Mean velocity (left) and turbulence kinetic energy (right) profiles
    at $x/D=1$ from 2-D simulations, 3-D simulations (at the mid $x$--$y$ plane,
    or $z/H=0$), and experiments \cite{Bachant2015-JoT}.}
